---
title: "Data Analysis Results"
author: "Itir Karac"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_caption: yes
    fig_width: 4
    fig_height: 4
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
  
```{r setup, include = FALSE}
knitr::opts_chunk$set(
collapse = TRUE,
comment = "#>",
fig.align = "center"
)
```

```{r}
library(reproducerTaskGra)
```

## Participant Demographics

```{r participant_demographics, fig.cap = "Fig. 1: Summary of demographic survey for participants" }
reproduce_barplot_participants()
```

## Statistical Data Analysis

### Functional Correctness

#### Descriptive statistics

```{r descriptive_stats_COR}
knitr::kable(reproduce_descriptive_stats_CORRECTNESS())
```

#### Plots
```{r, fig.cap = "Fig. 2. Violin plots for CORRECTNESS at both levels of Task Description Granularity. Data points are indicated as dots grouped into bins of width 5. Horizontal lines within the plots indicate 0.25, 0.50 and 0.75 quantiles." }
reproduce_violin_plot_CORRECTNESS()
```

```{r, fig.width = 8, fig.cap = "Fig. 3. Boxplots for CORRECTNESS shown separately on different tasks and sequences. Data points are indicated as dots grouped into bins of width 5. Horizontal lines within the plots indicate 0.25, 0.50 and 0.75 quantiles" }
reproduce_boxplot_CORRECTNESS()
```

#### Linear Mixed-effects Model
```{r}
reproduce_lmm_CORRECTNESS()
knitr::kable(reproduce_estimates_CORRECTNESS(), caption = "Estimates of fixed effects for CORRECTNESS")
```

####  Hypothesis Tests
```{r}
knitr::kable(reproduce_hypothesis_testing_CORRECTNESS(), caption = "Tests of fixed effects for CORRECTNESS")
```

####  Confidence Intervals
```{r}
knitr::kable(reproduce_confidence_intervals_CORRECTNESS(), caption = "Confidence intervals for estimates of fixed effects for CORRECTNESS")
```

####  Effect Size

#####  Esmated Marginal Means
```{r}
knitr::kable(reproduce_emmeans_CORRECTNESS(), caption = "Estimated Marginal Means for CORRECTNESS")
```


#####  Effect Size Based on Esmated Marginal Means
```{r}
knitr::kable(reproduce_emeans_effect_size_CORRECTNESS(), caption = "Effect Size Based on Estimated Marginal Means")
```
```{r, fig.cap = "Fig. 7. Profile plots of estimated marginal means for CORRECTNESS"}
reproduce_emmeans_profileplot_CORRECTNESS()
```


#### Assessment of Model Validity and Fit

##### Model Fit
```{r}
knitr::kable(reproduce_model_fit_statistics_CORRECTNESS(), caption = "Model fit statistics for CORRECTNESS")
```

##### Comparison of Alternative Models

### Functional Completeness

#### Descriptive statistics

```{r descriptive_stats_COMP}
knitr::kable(reproduce_descriptive_stats_COMPLETENESS())
```

#### Plots
```{r, fig.cap = "Fig. 5. Violin plots for COMPLETENESS at both levels of Task Description Granularity. Data points are indicated as dots grouped into bins of width 5. Horizontal lines within the plots indicate 0.25, 0.50 and 0.75 quantiles." }
reproduce_violin_plot_COMPLETENESS()
```

```{r, fig.cap = "Fig. 6. Boxplots for COMPLETENESS shown separately on different tasks and sequences. Data points are indicated as dots grouped into bins of width 5. Horizontal lines within the plots indicate 0.25, 0.50 and 0.75 quantiles" }
reproduce_boxplot_COMPLETENESS()
```

#### Linear Mixed-effects Model
```{r}
reproduce_lmm_COMPLETENESS()
knitr::kable(reproduce_estimates_COMPLETENESS(), caption = "Estimates of fixed effects for COMPLETENESS")
```

####  Hypothesis Tests
```{r}
knitr::kable(reproduce_hypothesis_testing_COMPLETENESS(), caption = "Tests of fixed effects for COMPLETENESS")
```

####  Confidence Intervals
```{r}
knitr::kable(reproduce_confidence_intervals_COMPLETENESS(), caption = "Confidence intervals for estimates of fixed effects for COMPLETENESS")
```

####  Effect Size
#####  Esmated Marginal Means
```{r}
knitr::kable(reproduce_emmeans_COMPLETENESS(), caption = "Estimated Marginal Means for COMPLETENESS")
```

#####  Effect Size Based on Esmated Marginal Means
```{r}
knitr::kable(reproduce_emeans_effect_size_COMPLETENESS(), caption = "Effect Size Based on Estimated Marginal Means")
```

```{r, fig.cap = "Fig. 7. Profile plots of estimated marginal means for COMPLETENESS"}
reproduce_emmeans_profileplot_COMPLETENESS()
```

#### Assessment of Model Validity and Fit

##### Model Fit
```{r}
knitr::kable(reproduce_model_fit_statistics_COMPLETENESS(), caption = "Model fit statistics for COMPLETENESS")
```

##### Comparison of Alternative Models

([Project Website](http://eatdd.oulu.fi))
